How to Avoid OOTA Without Really Trying

### 2024-09-15 paper/ootavacuous.tex
litmus2table.sh: Use \\qquad to get proper indentation
Based on Alan Stern's early by-hand change.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Nit: s/not to cause/to avoid/
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{listing}[tbp]
% Constructed by litmus2table.sh and modified by hand
{
\small
\begin{tabular}{r|l|l}
& \multicolumn{1}{c}{T0} & \multicolumn{1}{c}{T1} \\
\hline
1. &
\texttt{~int r0 = y} &
	\texttt{~int r1 = x} \\
2. &
\texttt{~if (r0 == 42)} &
	\texttt{~if (r1 == 42)} \\
3. &
\texttt{\qquad x = 42} &
	\texttt{\qquad y = 42} \\
4. &
\texttt{~else} &
	\texttt{~else} \\
5. &
\texttt{\qquad x = r0} &
	\texttt{\qquad y = r1} \\
\end{tabular}

\vspace{0.1in}
Condition (0:r0=42 $\wedge$ 1:r1=42)
sometimes satisfied.
}
\caption{OOTA Cycle}
\label{lst:OOTA Cycle}
\end{listing}

@@

Invented atomic loads are problematic:
\begin{quote}
\begin{verbatim}
int r0 = x;
int r1 = r0 * r0 + 2 * r0 + 1;
\end{verbatim}
\end{quote}
For values of \co{x} small enough not to cause overflow, the abstract machine is
guaranteed to produce a perfect square in \co{r1}.

>>>>

\begin{listing}[tbp]
@@ DisplayRunLitmus litmus/oota-ctrl.litmus @@
\caption{OOTA Cycle}
\label{lst:OOTA Cycle}
\end{listing}

@@

Invented atomic loads are problematic:
\begin{quote}
\begin{verbatim}
int r0 = x;
int r1 = r0 * r0 + 2 * r0 + 1;
\end{verbatim}
\end{quote}
For values of \co{x} small enough to avoid overflow, the abstract machine is
guaranteed to produce a perfect square in \co{r1}.
